Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-08 manuscript/draft_rsfmri.Rmd
test

```{r "To do", include=FALSE}
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines
# [ ] Swap mFD with logmFD ??
```

```{r "load packages", include=FALSE}

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8

@@

source('/data/gh_gr_agingandobesity_share/literature/methods/statistics/linear_models_course_rogermundry_2018/functions/glmm_stability.r')
source('/data/gh_gr_agingandobesity_share/literature/methods/statistics/linear_models_course_rogermundry_2018/functions/diagnostic_fcns.r')

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = ' ') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
#opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
#setwd(knitr::opts_knit$get("root.dir"))

>>>>

```{r "load packages", include=FALSE}
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8

@@

source('/data/gh_gr_agingandobesity_share/literature/methods/statistics/linear_models_course_rogermundry_2018/functions/glmm_stability.r')
source('/data/gh_gr_agingandobesity_share/literature/methods/statistics/linear_models_course_rogermundry_2018/functions/diagnostic_fcns.r')
```

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = ' ') # hide NA in tables
```
